Solutions to the potential for unintended conservation consequences of MPAs

### 2021-09-15 documents/03_marlin_paper.Rmd
pre visual commit

Empirically, how do you differentiate increase in catch from fishing harder vs increases in catch from rebuilding: rebuilding has to have a decrease at first

Marine protected areas (MPAs) are a growing part of the marine
conservation toolbox, with 7.4% of the world's oceans currently
protected and, and bodies such as the IUCN calling for 30% protection by
2030. Many of the largest of these MPAs are being implemented in the
form of "blue-water" MPAs largely covering pelagic ecosystems,
characterized by highly mobile species and fishing fleets using a
diverse mix of static and dynamic ocean features. These systems operate
very differently from the coastal areas where modern MPA design
practices have been developed. Pelagic systems are also characterized by
combinations of relatively abundant species targeted by fishing, such as
most tuna stocks, and highly threatened species caught as incidental
"bycatch" in targeted fishing operations, such as oceanic whitetip
sharks. Blue-water MPAs are increasingly being proposed specifically to
benefit these by-catch populations while minimizing losses or where
possible providing benefits to fisheries.

>>>>

<!-- Empirically, how do you differentiate increase in catch from fishing harder vs increases in catch from rebuilding: rebuilding has to have a decrease at first -->

Marine protected areas (MPAs) are a growing part of the marine
conservation toolbox, with 5.9% of the world's oceans currently in implemented MPAs [@grorud-colvert2021], and bodies such as the IUCN calling for 30% protection by
2030. Many of the largest of these MPAs are being implemented in the
form of large MPAs primarily covering pelagic ecosystems. These pelagic systems operate
very differently from the coastal areas where modern MPA design
practices have been developed, characterized by highly mobile species and fishing fleets using a
diverse mix of static and dynamic ocean features. These ecosystems
combinations of relatively abundant species targeted by fishing, such as
most tuna stocks, and highly threatened species caught as incidental
"bycatch" in targeted fishing operations, such as oceanic whitetip
sharks. Blue-water MPAs are increasingly being proposed specifically to
benefit these by-catch populations while minimizing losses or where
possible providing benefits to fisheries.
